Dynein project log

### 2016-12-31 thesis_stuff/thesis_stuff.tex
Add a paper on linker movement to thesis_stuff.tex.

>>>>

\subsection{Linker position in Post-powerstroke dynein, two Post-PS states?}
Insights into dynein motor domain function from a 3.3A crystal structure, Hugo Schmidt, Andrew P. Carter\\

A crystal structure of just the motor domain in a low-ATP-affinity conformation. Suggests that differences between their structure and a Dictyostelium ADP-bound structure suggest there is a difference between AAA1 apo/ADP states, suggesting at least two post-powerstroke states. The paper postulates that linker interacting with AAA5 is what kicks out ADP. They say that linker-AAA5 complex creates a low-nucleotide-affinity state.\\

They further suggest that nucleotide binding causes the linker to unbind AAA5 and rebind AAA2 on nucleotide binding. Thus AAA5-linker is post-powerstroke apo and AAA2-linker is ATP-bound (pre or post powerstroke?)\\

ATPases 2, 3, 4 mutation leads to decreased velocity.\\

\subsection{Linker pre-powerstroke conformation}
ATP hydrolysis cycle-dependent tail motions in cytoplasmic dynein
Kon T, Sutoh K

This paper supposedly talks about how the linker changes conformation on ATP binding.\\
